A comparative analysis of penalized linear mixed models in structured genetic data

### 2020-08-21 main.tex
4.1 - formatted variable selection table

\anna{Obviously these need to be formatted... just use TP rates - FP not adding much}\\

\anna{True positive rates}
\begin{verbatim}
structureX    xi    method      `round(mean(value), 2)` `round(sd(value), 2)`
 1 1d_linear     0     lasso                         0.25                   0.05
 2 1d_linear     0     lasso_pca10                   0.23                   0.05
 3 1d_linear     0     lmm_ggmix                     0.25                   0.05
 4 1d_linear     0     lmm_lasso                     0.25                   0.05
 5 1d_linear     0     plmm_lasso                    0.25                   0.05
 6 1d_linear     0.8   lasso                         0.23                   0.05
 7 1d_linear     0.8   lasso_pca10                   0.28                   0.05
 8 1d_linear     0.8   lmm_ggmix                     0.28                   0.05
 9 1d_linear     0.8   lmm_lasso                     0.28                   0.05
10 1d_linear     0.8   plmm_lasso                    0.290                  0.05
11 indep_subpops 0     lasso                         0.23                   0.05
12 indep_subpops 0     lasso_pca10                   0.21                   0.05
13 indep_subpops 0     lmm_ggmix                     0.22                   0.05
14 indep_subpops 0     lmm_lasso                     0.23                   0.05
15 indep_subpops 0     plmm_lasso                    0.23                   0.05
16 indep_subpops 0.8   lasso                         0.25                   0.05
17 indep_subpops 0.8   lasso_pca10                   0.36                   0.06
18 indep_subpops 0.8   lmm_ggmix                     0.38                   0.06
19 indep_subpops 0.8   lmm_lasso                     0.38                   0.06
20 indep_subpops 0.8   plmm_lasso                    0.39                   0.06
21 other         0     lasso                         0.37                   0.06
22 other         0     lasso_pca10                   0.36                   0.06
23 other         0     lmm_ggmix                     0.4                    0.06
24 other         0     lmm_lasso                     0.4                    0.06
25 other         0     plmm_lasso                    0.41                   0.06
26 other         0.8   lasso                         0.290                  0.06
27 other         0.8   lasso_pca10                   0.47                   0.06
28 other         0.8   lmm_ggmix                     0.61                   0.06
29 other         0.8   lmm_lasso                     0.580                  0.06
30 other         0.8   plmm_lasso                    0.580                  0.06
\end{verbatim}

>>>>

\anna{var selection results}
\begin{table}[H]
\centering
\begin{tabularx}{400pt}{cclYYY}
\toprule
$\eta$ & $\xi$ & \multicolumn{1}{c}{Method} & 1D Linear Admixture & Independent Subpopulations & Semi-Empirical \\ 
\midrule
\multirow{6}{*}{0.5} & \multirow{3}{*}{0} & Lasso & 0.25 (0.05) & 0.23 (0.05) & 0.37 (0.06) \\ 
& & PC-Lasso & 0.23 (0.05) & 0.21 (0.05) & 0.36 (0.06) \\ 
& & LMM-Lasso & 0.25 (0.05) & 0.23 (0.05) & 0.41 (0.06) \\
\cmidrule{2-6}
& \multirow{3}{*}{0.8} & Lasso & 0.23 (0.05) & 0.25 (0.05) & 0.29 (0.06) \\ 
& & PC-Lasso & 0.28 (0.05) & 0.36 (0.06) & 0.47 (0.06) \\ 
& & LMM-Lasso & 0.29 (0.05) & 0.39 (0.06) & 0.58 (0.06) \\ 
\bottomrule
\end{tabularx}
\label{tab:var_sel}
\caption{True positive rates, mean (SD), for different data types in the presence and absence of environmental confounding with coarse subpopulation structure and dichotomous-discordant environmental effects.}
\end{table}
